---
title: "Investigating Class docs"
author: 'Phoebe Guinn'
date: "1 July 2019"
output: html_document
---

##Language and Intersectionality of Gender and Class

###Loading Into Dataframe

```{r}
library(LexisNexisTools)
library(quanteda)
library(stringr)
library(ggplot2)

file_names <- list.files(pattern = ".txt", 
                        path = "~/Capstone/Extreme Class Articles", 
                        full.names = TRUE, recursive = TRUE, ignore.case = TRUE) %>%
  append(list.files(pattern = "Angela Rayner|Rebecca Long-Bailey|Margaret Jay|Tessa Jowell", 
                    path = "~/Capstone/Female Cabinet Articles", 
                    full.names = TRUE, recursive = TRUE, ignore.case = TRUE)) %>%
  append(list.files(pattern = "Alan Johnson|Bob Ainsworth|Tristram Hunt|Hilary Benn|Chuka Umunna", 
                    path = "~/Capstone/Male Cabinet Articles", 
                    full.names = TRUE, recursive = TRUE, ignore.case = TRUE))

mp_names <- str_extract(file_names, "([^/]+$)") %>%
  gsub("\\.TXT", "", .)

mp_class <- c("wc", "wc", "uc", "wc", "wc", "uc", "wc", "wc", "uc",
              "wc", "uc", "wc", "wc", "uc", "uc", "uc")


class_frame <- data.frame()
for (i in 1:length(file_names)) {
  LNToutput <- lnt_read(x = file_names[i], extract_paragraphs = FALSE, verbose = F)
  temp <- data.frame(LNToutput@articles)
  temp$mp <- rep(mp_names[i], nrow(temp))
  temp$class <- rep(mp_class[i], nrow(temp))
  class_frame <- rbind(class_frame, temp)
}

table(class_frame$class)
table(class_frame$mp)
```

###Finding Key Features

-Just keep features within wc dictionary: HGI 
-Following keys decided through literature review
Virtue: 719 words indicating an assessment of moral approval or good fortune, especially from the perspective of middle-class society
Vice: 685 words indicating an assessment of moral disapproval or misfortune
Means: 244 words denoting objects, acts or methods utilized in attaining goals
Need: 76 words related to the expression of need or intent
Persist: 64 words indicating "stick to it" and endurance
IPAdj: 117 adjectives referring to relations between people, such as "unkind, aloof, supportive"
IndAdj: 637 adjectives describing people apart from their relations to one another, such as "thrifty, restless"
Ought: 26 words indicating moral imperative
SklOth: 158 other skill-related words
RcEthic: Ethics, 151 words of values concerning the social order
RspTot: Respect is the valuing of status, honor, recognition and prestige
And, https://www.macmillandictionary.com/thesaurus-category/british/social-class-and-attitudes-to-class

```{r}

classdict_table <- read.csv("~/Capstone/Dictionaries/GI-ClassPotential.csv",
                            header = T, fill = T, stringsAsFactors = F, blank.lines.skip = T)

classdict <- dictionary(list(
  virtue = classdict_table[,1],
  vice = classdict_table[,2],
  need = classdict_table[,3],
  means = classdict_table[,4],
  persist = classdict_table[,5],
  ought = classdict_table[,6],
  InterPersAdj = classdict_table[,7],
  IndAdj = classdict_table[,8],
  ethics = classdict_table[,9],
  respect = classdict_table[,10],
  skills = classdict_table[,11],
  class_rel = classdict_table[,12]
))

#form into corpus
class_corp <- corpus(class_frame$Article)
docvars(class_corp, "class") <- class_frame$class
docvars(class_corp, "mp") <- class_frame$mp

#use following dfm to apply to textstat_keyness() and kwic() to decide which keys to keep in dictionary
class_dict_res <- dfm(class_corp, groups = "class", remove = stopwords("english"), dictionary = classdict[-c(7,8)]) %>%
  dfm_weight(scheme = "prop")
dfm(class_corp, remove_punct = T, remove = stopwords("english")) %>%
  dfm_select(classdict[c(6:8,12)]) %>%
  dfm_group(groups = "class") %>%
  textstat_keyness("wc", measure = "chi2") %>%
  textplot_keyness(n=20)
#estate referring to place growing up, especially for members such as David Lammy, Angela Rayner

#not using need (interest, hope) since this might refer more to how the person presents themself rather than being presented. Or maybe not taken seriously when talking of what country needs, focus on other things. Such as results from 7,8,12: class, background, estate. Not means, no difference. Persist doesnt give much information. Neither does skills. 
#Ethics, interesting but leads to just all the bad things each side do. 
#keep vice, virtue, adjs, class, respect (interesting)
```

###Using Wordscores to map word usage / types of words used for each gender/class

```{r}
#make shorter gender address dictionary 
gendered_words <- c("FEMALE", "FEMININE", "GIRL", "WOMAN", "WOMANLY", "WOMEN", "BOY", "GENTLEMAN", "GUY", "MALE", "MAN ", "MANLY", "MASCULINE", "MEN ")
relations <- c("AUNT", "BRIDE", "COUSIN", "DAUGHTER", "GRANDMA", "GRANDMOTHER", "GRANNY", "MOTHER", "MUM", "MUMMY", "NIECE", "SISTER", "WIDOW", "WIFE", "BROTHER", "DAD", "DADDY", "FATHER", "GRANDAD", "GRANDFATHER", "GRANDPA", "GROOM", "HUSBAND", "NEPHEW", "SON", "UNCLE")
address_dict2 <- dictionary(list(gendered_words = gendered_words, relations = relations))

#make whole dictionary
comb_dict <- dictionary(c(as.list(classdict[c(6:8,12)]), as.list(address_dict2)))
#make dfm for each mp
#1 = wc, men, 2 = uc, fem   
class_dfm <- dfm(class_corp, select = comb_dict, groups = "mp") %>%
  dfm_trim(min_termfreq = 5)
docvars(class_dfm, "class") <- c(1,1,1,2,1,1,2,2,1,1,2,2,1,1,2,2)
docvars(class_dfm, "gender") <- c(1,2,1,1,1,1,2,1,2,2,2,2,2,1,2,1)
                             
#apply wordscores
ws_c <- textmodel_wordscores(class_dfm, docvars(class_dfm, "class") , smooth=.5)
ws_g <- textmodel_wordscores(class_dfm, docvars(class_dfm, "gender") , smooth=.5)

#put wordscores into df which will then be plotted
plot_words <- as.data.frame(coef(ws_c))
plot_words$gender_score <- coef(ws_g)
colnames(plot_words)[1] <- "class_score"

#highlight which words most interesting in plot
specific_words <- grepl("feminine|masculine|hardy|daring|unruly|accent|abrasive|rotten|immature|voluntary|charitable|rich|humanitarian|inspirational|husband|wife|mother|father|grandmother|manly|woman|man", rownames(plot_words))

plot_words %>%
  ggplot(aes(x = class_score, y = gender_score)) +
  geom_text(data = plot_words[!specific_words,], label=rownames(plot_words[!specific_words,]), colour = "darkgrey") +
  geom_text(data = plot_words[specific_words,], label=rownames(plot_words[specific_words,]), colour = "black")

# let's look at the most discriminant word
sw <- sort(coef(ws_c))
names(head(sw, n=60))
tail(sw, n=60)

```

Not good/reliable at rescoring/predicting other politicians (presumably because either training data too small, or that most cabinet ministers are of the same class)





