---
title: "Cleaning data, sorting into dataframe, and assigning topic"
author: 'Phoebe Guinn'
date: "22 May 2019"
output: html_document
---

###Preparing:
- Download from Lexis Nexis 
- Add into data frame with data, newspaper, label mp name and gender

```{r, eval = FALSE}
library(LexisNexisTools)
library(quanteda)
library(stringr)
library(dplyr)

fem_files <- list.files(pattern = ".txt", 
                        path = "C:/Users/phoeb/OneDrive/Documents/Capstone/Female Cabinet Articles", 
                        full.names = TRUE, recursive = TRUE, ignore.case = TRUE)
fem_names <- str_extract(fem_files, "([^/]+$)") %>%
  gsub("\\.TXT", "", .)

fem_frame <- data.frame()
for (i in 1:length(fem_files)) {
  LNToutput_fem <- lnt_read(x = fem_files[i], extract_paragraphs = FALSE)
  fem_temp <- data.frame(LNToutput_fem@articles)
  fem_temp$date <- LNToutput_fem@meta$Date
  fem_temp$newspaper <- LNToutput_fem@meta$Newspaper
  fem_temp$mp <- rep(fem_names[i], nrow(fem_temp))
  fem_frame <- rbind(fem_frame, fem_temp)
}
fem_frame$gender <- rep("female", nrow(fem_frame))
rm(LNToutput_fem, fem_temp, fem_files, fem_names)

male_files <- list.files(pattern = ".txt", 
                         path = "C:/Users/phoeb/OneDrive/Documents/Capstone/Male Cabinet Articles",
                         full.names = TRUE, recursive = TRUE, ignore.case = TRUE)
male_names <- str_extract(male_files, "([^/]+$)") %>%
  gsub("\\.TXT", "", .)

male_frame <- data.frame()
for (i in 1:length(male_files)) {
  LNToutput_male <- lnt_read(x = male_files[i], extract_paragraphs = FALSE)
  male_temp <- data.frame(LNToutput_male@articles)
  male_temp$date <- LNToutput_male@meta$Date
  male_temp$newspaper <- LNToutput_male@meta$Newspaper
  male_temp$mp <- rep(male_names[i], nrow(male_temp))
  male_frame <- rbind(male_frame, male_temp)
}
male_frame$gender <- rep("male", nrow(male_frame))
rm(LNToutput_male, male_temp, male_files, male_names)

```

###Sort files into topics: 
Using Lexicoder Topic Dictionary (Albugh et al., 2013)
Add  topi/policy issue as column in frame.

```{r, eval = FALSE}
#Healthcare, Education, Social Welfare, Civil Rights, Macroeconomic, Defence, Foreign Trade, International_affairs

policydict_raw <- scan("topicdict.csv", what = c("character"), sep = "\n", strip.white = F) 
#find lines with dictionary codes
grep("cnode", policydict_raw)
policydict <- dictionary(list(civil_rights = policydict_raw[85:171],
                              healthcare = policydict_raw[174:299],
                              education = policydict_raw[302:339], 
                              social_welfare = policydict_raw[342:405],
                              macroeconomics = policydict_raw[2:82],
                              defence = policydict_raw[408:459], 
                              #foreign_trade = policydict_raw[452:482],
                              intl_affairs = policydict_raw[495:559],
                              crime = policydict_raw[562:632]
                              ))
rm(policydict_raw)

# combine all articles and set tokens to sets of 1,2 and 3 words (how long entries in dictionary are)
full_df <- rbind(fem_frame, male_frame)[,-1]
all_toks <- tokens(full_df$Article, what="word", ngrams=1:3)

#apply topic dictionary
topicdf <- dfm(all_toks, tolower = T, remove_punct = T) %>%
  dfm_weight(scheme = "prop") %>%
  dfm_lookup(dictionary = policydict, valuetype = "glob") %>%
  convert(to = "data.frame")
#find max column entry (topic feature count) and set article to this topic 
z <- max.col(as.matrix(topicdf[,-1]), ties.method = "random")
full_df$topic <- names(topicdf)[z+1]
#set to 'None' where no features
row_sub <- apply(topicdf[,-1], 1, function(row) all(row == 0 ))
full_df$topic[row_sub] <- 'None'
```

###Tidy newspaper names and fix one quoting problem

```{r, eval = FALSE}

full_df[20685,1] <- gsub('\\\\', "\\", full_df[20685,1])


full_df$newspaper[full_df$newspaper %in% 
                  c("Daily Mail (London)", "Mail on Sunday (London)", "MAIL ON SUNDAY", "DAILY MAIL (London)",
                    "MAIL ON SUNDAY (London)", "MailOnline")] <- "The Daily Mail"

full_df$newspaper[full_df$newspaper %in% 
                  c("Independent Magazine", "Independent on Sunday (London)", "Independent.co.uk",
                    "The Independent - Daily Edition", "The Independent (London)", "The Independent (United Kingdom)",
                    "The Independent on Sunday")] <- "The Independent"

full_df$newspaper[full_df$newspaper %in% c("The Observer (London)")] <- "The Observer"

full_df$newspaper[full_df$newspaper %in% 
                  c("telegraph.co.uk", "The Daily Telegraph (London)", "The Daily Telegraph (LONDON)",
                    "THE DAILY TELEGRAPH(LONDON)", "The Sunday Telegraph (LONDON)",
                    "The Sunday Telegraph (London)")] <- "The Telegraph"

full_df$newspaper[full_df$newspaper %in% 
                  c("The The Sunday Times (London)", "The Times (London)", "The Sunday Times (London)",
                    "Sunday Times (London)", "Copyright 2004 Times Newspapers Limited")] <- "The Times"

full_df$newspaper[full_df$newspaper %in% c("Daily Mirror", "mirror.co.uk", "Sunday Mirror", "The Mirror")] <- "The Daily Mirror"

full_df$newspaper[full_df$newspaper %in% c("The Sun (England)")] <- "The Sun"

full_df$newspaper[full_df$newspaper %in% 
                  c("Guardian.com", "Guardian.com.", "The Guardian", "The Guardian - Final Edition",
                    "The Guardian(London)", "The Guardian (London)", "The Guardian (London) - Final Edition")] <- "The Guardian"

full_df$newspaper[full_df$newspaper %in% c("Daily Star", "Daily Star Sunday")] <- "The Daily Star"

full_df$newspaper[full_df$newspaper %in% c("Express Online", "Sunday Express", "The Express")] <- "The Express"

full_df <- full_df[!full_df$newspaper %in% 
                     c("Arts & Book Review", "Saturday Magazine", "Sunday Business", "The New Review", "The Observer", "The Daily Star"),]

# These removed so that the many articles talking about football are removed and don't alter results
full_df <- full_df[!grepl("(c|C)hampionship|(C|c)eltic|(F|f)ootball", full_df$Article),]

```

Write the full frame to file, to be used to subsequent analyses. 
(eval = F set so doesn't do this every time html output knitted)

```{r, eval = FALSE}

write.table(full_df, file = "articlesdf", append = F)

```


Albugh, Q., Sevenans, J. and Soroka, S. (2013). Lexicoder Topic Dictionaries, June 2013 versions, McGill University, Montreal, Canada. (available at lexicoder.com)



